---
title: "Data 607 Assignment Week 7"
author: "Ajay Arora"
date: "September 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(XML)
library(plyr)
library(dplyr)
#library(xml2)
library(RCurl)
library(httr)
library(rvest)
library(kableExtra)
#library(jsonlite)
require(RJSONIO)
library(DT)
library(jsonlite)
library(purrr)
library(data.table)
```

Reference: https://www.datacamp.com/community/tutorials/r-data-import-tutorial#xml
           
           https://www.tutorialspoint.com/r/r_xml_files.htm
           
           https://subscription.packtpub.com/book/big_data_and_business_intelligence/9781783989065/1/ch01lvl1sec11/reading-xml-data
           
           https://www.kaggle.com/robertoruiz/how-convert-json-files-into-data-frames-in-r

```{r}
##Read html document
url1 = "https://raw.githubusercontent.com/AjayArora35/Data-607-Assignment-Week-7/master/Source Week Assignment 7.html"
download.file(url1, destfile = "scrapedpage1.html", quiet=TRUE)
doc1 = htmlParse("scrapedpage1.html", encoding = "ISO-8859-1")
# For debugging doc1

z1 = as.data.frame(readHTMLTable(doc1, stringsAsFactors = FALSE, header = TRUE))

#Rename the columns becuase they contain "NULL."
names(z1)[1] <- "title"
names(z1)[2] <- "author"
names(z1)[3] <- "year"
names(z1)[4] <- "price"
names(z1)[5] <- "_category"

z1 %>% kable() %>%  kable_styling()
```

```{r}
url2 = "https://raw.githubusercontent.com/AjayArora35/Data-607-Assignment-Week-7/master/Source Week Assignment 7.xml"

download.file(url2, destfile = "scrapedpage1.xml", quiet=TRUE)
doc2 = xmlParse("scrapedpage1.xml", encoding = "ISO-8859-1")
#For debugging doc2

rootNode <- xmlRoot(doc2)
#rootNode[1] 

xml <- ldply(xmlToList(rootNode), data.frame)
#For debugging xml

z2 <- xml %>% select(-c(.id, title..attrs))
colnames(z2) <- c('title','author','year','price', '_category', 'author.1', 'author.2', 'author.3', 'author.4')

z2[1:4,] %>% kable() %>%  kable_styling()
```

```{r}

url3 <- "https://raw.githubusercontent.com/AjayArora35/Data-607-Assignment-Week-7/master/Source Week Assignment 7.json"

pop_proj_data_df <- RJSONIO::fromJSON(url3)

#Since we get back a list, lets convert to an array and construt a matrix then convert to data frame
arr <- array(pop_proj_data_df[[1]]$book)

#Get number of items in list
iterations <- length(pop_proj_data_df[[1]]$book)
#Establish matrix to construct our data frame 
m <- matrix(ncol = 5, nrow = iterations)

row <- 1

#Construct matrix and populate with list items 
for(i in 1:iterations){
  for ( j in arr[i]) { 
    if(j$`-category` != ''){
      m[row, 5] <- (j$`-category`)
    }
    if(j$year != ''){
      m[row, 3] <- (j$year)
    }
    if(j$price != ''){
      m[row, 4] <- (j$price)
    }
    if(j$title[2] != ''){
      m[row, 1] <- (j$title[2])
    }
    a <- paste0(j$author, collaspe = ' ')
    if(j$author[1] != ''){
      m[row, 2] <- toString(a)
    }

    row <- row + 1
    
  }
  
}
#For debugging m

z3 <- data.frame(m)
x <- c('title','author','year','price', '_category')
colnames(z3) <- x
z3 %>% kable() %>%  kable_styling()
```

##Data frames are different for XML compared with HTML and JSON.
## The HTML file produced a table where the multiple authors were listed in a single column.  The XML file produced a table where the multiple authors were separated into different columns.  Lastly, JSON file produced a list, where the authors were all together, and I decided to produce a table where all the authors were stored in a single column, similar to HTML.  